Report - Latest Rodent Data

### 2019-02-27 evaluation.Rmd
Update evaluation.Rmd
adding in the evalution plot

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
  species <- rodent_spp(set = "evalplot")
  fcasts <- read_casts() %>%
            select_casts(species = species, level = "Controls") %>%
            append_observed_to_cast()
  fcast_errors <- measure_cast_error(fcasts)
  hcasts <- read_casts(cast_type = "hindcasts") %>%
            select_casts(species = species, level = "Controls") %>%
            append_observed_to_cast()
  hcast_errors <- measure_cast_error(hcasts)
```

@@

## How have the models done historically?

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

@@

```{r recent_eval, echo=FALSE, fig.width=7, fig.height=7}
plot_err_lead_spp_mods()
```

## How would have the models done historically?

Here, we evaluate the models' abilities to hindcast the historic data.

### 2019-02-27 index.Rmd
adding in the evalution plot

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
plot_cast_ts()
```

@@

```{r speciesforecasts, echo=FALSE, message=FALSE, warning=FALSE}
plot_cast_point()
```

>>>>

```{r, echo=FALSE, fig.width=8, fig.height=6}
plot_cast_ts()
```

@@

```{r speciesforecasts, echo=FALSE}
plot_cast_point()
```

### 2019-02-27 report.Rmd
adding in the evalution plot

Here's the most recent actual data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_cast_point(with_census = TRUE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_cast_point(with_census = TRUE, level = "All")
```

>>>>

Here's the most recent actual data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE}
plot_cast_point(with_census = TRUE)
```

```{r, echo=FALSE}
plot_cast_point(with_census = TRUE, level = "All")
```
